### 2012-11-17 inst/examples/reed-example.Rmd
updated examples using sequential approach
SDP using kernlab

```{r libraries}
require(pdgControl)
require(ggplot2)
opts_knit$set(upload.fun = socialR::flickr.url)
```

### Beverton-Holt function

Simulate some training data under a stochastic growth function with standard parameterization,

``` {r stateeqn}
f <- BevHolt
p <- c(1.5,.05)
K <- (p[1]-1)/p[2] 
```

Parameter definitions

```{r}
x_grid = seq(0, 1.5 * K, length=101)
T <- 40
sigma_g <- 0.1
x <- numeric(T)
x[1] <- 1
```

Noise function, profit function
```{r}
z_g <- function() rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
profit <- profit_harvest(1,0,0)
```

Simulation

```{r}
for(t in 1:(T-1))
  x[t+1] = z_g() * f(x[t], h=0, p=p)
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=.5, l=1.5))
```

Gaussian Process inference from this model.  True model shown in red.

```{r}
df <- data.frame(x=X, y=gp$Ef, ymin=(gp$Ef-2*sqrt(abs(diag(gp$Cf)))), ymax=(gp$Ef+2*sqrt(abs(diag(gp$Cf)))))
true <- data.frame(x=X, y=sapply(X,f, 0, p))
require(ggplot2)
ggplot(df)  + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x,y)) + geom_point(data=obs, aes(x,y)) +
  geom_line(data=true, aes(x,y), col='red', lty=2)
```

@@

```{r}
V <- sqrt(diag(gp$Cf))
matrices_gp <- lapply(h_grid, function(h){
  F <- sapply(x_grid, function(x) dnorm(x, gp$Ef-h, V))
  F <- rownorm(F)
})
```

>>>>

```{r include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
```

```{r}
require(pdgControl)
require(nonparametricbayes)
require(ggplot2)
```

```{r results="hide"}
knit("beverton_holt_data.Rmd")
```

@@

```{r}
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=1, l=1.5))
plot.gpfit(gp)
```

Solution using `kernlab`

```{r}
library(kernlab)
#gp <- gausspr(obs$x, obs$y, kernel="rbfdot", kpar=list(sigma=0.5), fit=FALSE, scaled=FALSE, var=.09)
gp <- gausspr(obs$x, obs$y, kernel="rbfdot", scaled=FALSE, var=.01)
Ef <- predict(gp, X)
```

Manually get the covariance, $K(x_*, x_*) - K(x_*, x)(K(x, x) - \sigma_n^2\mathbb{I})^{-1}K(x,x_*)$.

```{r}
var <- gp@kcall$var
var <- 9
Inv <- solve(kernelMatrix(kernelf(gp), xmatrix(gp)) + diag(rep(var, length = length(xmatrix(gp)))))
Cf <- kernelMatrix(kernelf(gp), as.matrix(X)) - 
  kernelMult(kernelf(gp), as.matrix(X), xmatrix(gp),  Inv) %*% 
  kernelMatrix(kernelf(gp), xmatrix(gp), as.matrix(X))
```

```{r}
require(ggplot2)
dat <- data.frame(x=X, y=(Ef), ymin=(Ef-2*sqrt(diag(Cf))), ymax=(Ef+2*sqrt(diag(Cf))))    
ggplot(dat) + 
  geom_ribbon(aes(x=x,y=y, ymin=ymin, ymax=ymax), fill="grey80") +
  geom_line(aes(x=x,y=y), size=1) +
  geom_point(data=obs,aes(x=x,y=y)) + 
  scale_y_continuous(name="output, f(x)") + xlab("input, x") 
```

@@

```{r}
V <- sqrt(diag(Cf))
matrices_gp <- lapply(h_grid, function(h){
  F <- sapply(x_grid, function(x) dnorm(x, Ef-h, V))
  F <- rownorm(F)
})
```
